Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-22 Docs/TODAES/paper.tex
fixing reference to table
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

To perform the experiments, some benchmarks provided by Mann {\it et al.}~\cite{Mann2007} were used, as shown in Table~\ref{Description-of-Benchmarks}. The nodes in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area. The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}. The clustering and fuzzy benchmarks are designed from Mann {\it et al.}~\cite{Mann2007} and are significantly large benchmarks. From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).

>>>>

To perform the experiments, some benchmarks provided by Mann {\it et al.}~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}. The nodes in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area. The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}. The clustering and fuzzy benchmarks are designed from Mann {\it et al.}~\cite{Mann2007} and are significantly large benchmarks. From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).
